surfing

### 2021-08-22 inst/surfing.Rmd
issue #107 refers: now pwa() only operates for a single Brazilian

```{r surfing2, cache=TRUE}
surfing2 <- hyper2()
for(v in o){
   venue <- v[1]  # first entry is venue
   r <- v[-1] 
   numberretained <- sum(!(r %in% remove))
   if(numberretained > 1){
     r <- r[!(r %in% remove)]
     jj <- race(r)
     surfers <- pnames(jj)
     if(any(nationality(surfers) == "BRA")){
       if((beachtype(venue)=="point") | (beachtype(venue) == "beach")){
         jj %<>% pwa(surfers[nationality(surfers)=="BRA"],"Brazilian_beachtype")
       }    	     
     } 
     surfing2 %<>% sum(jj)
   }
}	
summary(surfing2)
```

>>>>

```{r surfing2, cache=TRUE}
surfing2 <- hyper2()
for(v in o){
   venue <- v[1]  # first entry is venue
   r <- v[-1] 
   numberretained <- sum(!(r %in% remove))
   if(numberretained > 1){
     r <- r[!(r %in% remove)]
     jj <- race(r)
     surfers <- pnames(jj)
     if(sum(nationality(surfers)=="BRA")==1){	
       if((beachtype(venue)=="point") | (beachtype(venue) == "beach")){
         jj %<>% pwa(surfers[nationality(surfers)=="BRA"],"Brazilian_beachtype")
       }
     }
     surfing2 %<>% sum(jj)
   }
}	
summary(surfing2)
```
